\documentclass[11pt]{article}
\usepackage{psfig}
\usepackage{latexsym}
\usepackage{amsfonts}
\usepackage{amsmath}

\setlength{\textheight}{8.5in}
\setlength{\textwidth}{6.0in}
\setlength{\headheight}{0in}
\addtolength{\topmargin}{-.5in}
\addtolength{\oddsidemargin}{-.5in}

\input{preamble.tex}
\begin{document}

\lecture{5}{January 25, 2018}{Arpita Patra}{Pranshu Gaba}

%%%% body goes in here %%%%

\section{Introduction}

In the last lecture, we looked at computational security. We made the definitions of PPT/negligible function precise in terms of security parameter \(n\). We looked at the semantic and the indistinguishability based definitions of security.

Now we will look at the pseudorandomness and PRGs. We will find a construcction for ind-secure scheme. We will make use of reduction-based proofs to prove that if PRGs exist, then a construction is secure according to ind definition. Finally, we will discuss the short comings of the current construction/definition, and try to come up with a better defintion.  

\section{Pseudorandom Generators (PRGs)}
\(G\) is a PRG if for every PPT \(D\), there is a negligible function \negl\ such that

\[ \lvert \mathrm{Pr}[D(r) = 1] - \mathrm{Pr} [D(G(s)) = 1] \rvert \le \mathsf{negl}(n) \]


\section{PRG can be cracked by an unbounded adversary}

\section{Existence of PRGs}
We assume that PRGs exist. It has neither been proven, nor disproven, although it is strongly believed that they exist.

\section{Stream Ciphers}
%This is due to \cite{lamport94} \footnote{footnotes working fine}
\section{One-way functions}
Functions that are ``easy to compute'' but almost always ``difficult to invert''.

\subsection{The Inverting Experiment}
Experiment \(\mathsf{Invert}_{\mathcal{A},f} (n)\)


\subsection{Mathematical Formulation}

Function \(f\) is a {\sf one-way function}  if the following two conditions hold:
\begin{itemize}
\item Easy to compute: for every \(x \in \{0, 1\}^*\), \(f(x)\) can be computed in \poly \((n)\) time.
\item Hard to invert: For every PPT algorithm \(A\), there is a negligible function \negl\((n)\) such that

  \[ \mathrm{Pr}(\mathsf{Invert}_{\mathcal{A}, f} (n) = 1) \le \mathsf{negl}(n) \approx \mathrm{Pr} _{x \leftarrow \{ 0, 1\}^n} [A f(x), 1^n) \in f^{-1} (f(x))] \le \mathsf{negl}(n) \]
\end{itemize}
\section{Reduction-based Proofs}


\begin{thebibliography}{9}

\bibitem{lamport94}
  Jonathan Katz, Yehuda Lindell,
  \textit{Introduction to Modern Cryptography},
  CRC Press, Taylor \& Francis Group,
  2nd edition,
  2015.
  
\end{thebibliography}




\end{document}
